---
output:
  md_document:
    variant: markdown_github
---

[GMACS]: https://github.com/GMACS-project/GMACS_Assessment_code/tree/main/GMACS/Latest_Version


[![GitHub release (latest by
date)](https://img.shields.io/github/release/GMACS-project/gmr)](https://github.com/GMACS-project/gmr/releases)


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# gmr - R package to work with a Generalized size-structured Model for Assessing Crustaceans **_GMACS_**

`gmr` is an R package providing tools to work with *[GMACS]*, a generalized size-structured assessment model for Crustaceans. Specifically, it includes an extensive library of functions developed to build and run GMACS for one or several crustacean stock(s) and to plot outputs of the model.

## Installation

To install the `gmr` package, the [`devtools`](https://cran.r-project.org/web/packages/devtools/index.html) and [`gdata`](https://cran.r-project.org/web/packages/gdata/index.html) packages are required.

```{r, eval=FALSE}
    if(!require("devtools"))
        install.packages("devtools")
    if(!require("devtools"))
        install.packages("gdata")

    # Install development version from Github
    .DirSrc <- "GMACS-project/gmr"
    devtools::install_github(.DirSrc)
```

Now you can load the package and inspect the functions:

```{r, eval=FALSE}
    # Load the gmr package
    library(gmr)
    # Explore function
    plot_growth
```

Using the functions requires output from the General Model for Assessing Crustacean Stocks (GMACS) which is described in the [GMACS] repo.
